### 2014-12-31 paper_10_intro.tex
added PROMISE Data repo

@@

\cite{Marcus2010}

>>>>

Software development produces many value pieces of datum that can be analyzed
\cite{Marcus2010}. Just a few of the pieces of datum are:
email communication, bugs, fixes, source code, version control system histories,
process information, and test data.  Examples of this type of data
can be found in the PROMISE Data Repository \cite{promise12}.

@@
